Reproducible development environments with rix

### 2024-01-30 paper.qmd
load rix
hiding messages

On versions of R released after version 3.6, these two lines return the
following vector, `r set.seed(1234);sample(seq(1, 10), 5);set.seed(NULL)`, in
versions prior to 3.6, the result will be different. This is a documented change
as shown in the R version 3.6 release
notes.^[https://stat.ethz.ch/pipermail/r-announce/2019/000641.html]

@@

```{r}
path_subshell <- tempdir()

@@

```{r}
rix_init(
   project_path = path_subshell,
   rprofile_action = "overwrite",
   message_type = "simple"
 )
```

@@

```{r}
out_subshell <- with_nix(
    expr = function(){
      set.seed(1234)
      a <- sample(seq(1, 10), 5)
      set.seed(NULL)
      return(a)
    },
    program = "R",
    exec_mode = "non-blocking",
    project_path = path_subshell,
    message_type = "simple"
  )

@@

>>>>

```{r, include = FALSE}
set.seed(1234)
out_r <- sample(seq(1, 10), 5)
set.seedt(NULL)
```

On versions of R released after version 3.6, these two lines return the
following vector: `r out_r`, but in versions prior to 3.6, the result will be
different. This is a documented change as shown in the R version 3.6 release
notes.^[https://stat.ethz.ch/pipermail/r-announce/2019/000641.html]

@@

```{r, include = FALSE}
library(rix)

path_subshell <- tempdir()

path_subshell <- tempdir()

@@

```{r, eval = F}
rix_init(
   project_path = path_subshell,
   rprofile_action = "overwrite",
   message_type = "simple"
 )
```

```{r, include = F}
rix_init(
   project_path = path_subshell,
   rprofile_action = "overwrite",
   message_type = "simple"
 )
```

@@

```{r, eval = F}
out_subshell <- with_nix(
    expr = function(){
      set.seed(1234)
      a <- sample(seq(1, 10), 5)
      set.seed(NULL)
      return(a)
    },
    program = "R",
    exec_mode = "non-blocking",
    project_path = path_subshell,
    message_type = "simple"
  )

@@

```{r, include = FALSE}
out_subshell <- with_nix(
    expr = function(){
      set.seed(1234)
      a <- sample(seq(1, 10), 5)
      set.seed(NULL)
      return(a)
    },
    program = "R",
    exec_mode = "non-blocking",
    project_path = path_subshell,
    message_type = "simple"
  )

We should say that `rix_init()` and `with_nix()` print many status messages to
the console while running, which we don't show here for space reasons.
